Contracts for Contracts

### 2023-02-05 paper.tex
misc

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
  \item We propose to add temporal and higher-order contracts to smart contract
    languages to improve the safety and reliability. We use Solidity to
    demonstrate our proposal.
  \item We present the core language ``Contract Solidity'' with our
    proposed extension, including its syntax, formal semantics, and soundness.
  \item We examine a number of real-world cases and show that our proposal is
    effective in improving safety and reliability.
  \item We implement our approach on top of the existing Solidity compiler and shows
    that its runtime overhead is marginal.
\end{itemize}

@@

@@

>>>>

\todo{allows interesting programming idioms to be expressed}

\subsubsection*{\textbf{Contributions}} This paper makes the following contributions:
\begin{itemize}
  \item We propose an conservative linguistic extension to Solidty,
    namely the temporal and higher-order contracts to improve the safety and
    reliability.
  \item We present the core language ``Contract Solidity'' with our
    proposed extension, including its syntax, formal semantics, and soundness.
  \item We examine a number of real-world cases and show that our proposal is
    effective in improving safety and reliability.
  \item We implement our approach on top of the existing Solidity compiler and shows
    that its runtime overhead is marginal, therefore practical to use.
\end{itemize}

@@

\todo{why modifier isn't enough}

@@

core calculus of Solidity-like languages \cite{Sergey2021, DBLP:conf/esorics/BartolettiGM19, DBLP:conf/fc/CrafaPZ19}
